The \frb\ Campaign: A Multi-Telescope Burst Detection and Implications for the FRB Population

### 2017-04-11 repeater-vladata.tex
working on new questions

>>>>

**
Open issues:
- How to discuss Arecibo weird burst results and "true" DM
-- earlier results are better stated as a change in profile shape with frequency. Just as for precision timing of pulsars. Could go with that for VLA. Error in estimate of DM caused by freq-dep pulse shape. "frequency evolution".
-- how to motivate use of dm=560.5? no real need to if we focus on broad band result over delta dm.
- Jason's Arecibo burst flux seems low
-- radiometer eqn for for peak flux averaged over 5 ms. 2 ms diluted to 5 ms, so peak flux down by 2/5.
- Frequency-dependent burst rate would be cool, but needs Arecibo L-band burst energies
-- burst rate is best for daniele's paper. laura and others too.
- How much detail in a table of obs times?
-- put as much in as feasible. consider long term utility
- GBT and other observations useful to include if no overlap?
